\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
stylistic changes

This paper is organized as follows. In Section~\ref{sec:background}, we first describe related work in this area. In Section~\ref{sec:survey}, we present details of the online survey including information about the types of trajectories and environments used. Section~\ref{sec:raw_results} presents the results from the survey and analysis, including the trajectory features used for classification and the classification approaches used with the data. In Section~\ref{sec:conclusion}, we conclude with a discussion of how our results could be used to design motion planners that generate more human-acceptable trajectories. 
\begin{figure}
\centering
\begin{minipage}[][][s]{0.45\columnwidth}
\centering
\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{1}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{2}}
\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{3}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{4}}
\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{5}}
(a)
\end{minipage}
\hfill
\begin{minipage}[][][s]{0.45\columnwidth}
\centering
\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{1}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{2}}
\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{3}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{4}}
\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{5}}
(b)
\end{minipage}
\caption{Example trajectory snapshots for motions that survey participants rated (a) highly and (b) poorly. In (b) the hand of the robot ducks under the table in between the first and middle snapshot.}\label{fig:example_trajectory}
\end{figure}

@@

\begin{table}
\label{tab:feature_description}
\scalebox{0.9}{
\centering
\begin{tabular}{p{0.3\columnwidth}|p{0.2\columnwidth}|p{0.5\columnwidth}}
\hline
Feature Name & Metric & Feature Description \\
\hline
path\_length, smoothness, clearance, max\_lin\_acc, joint\_limit\_distance & Joint-space & Features discussed in Section~\ref{subsec:traj_feat} computed on joint-space trajectory \tj{}\\
\hline
[link]\_length, [link]\_smoothness, [link]\_max\_curvature, [link]\_lin\_acc, [link]\_quat\_dist & Cartesian & Features discussed in Section~\ref{subsec:traj_feat} computed on 3D cartesian path traced by [link] in \tj{}\\
\hline
h\_[link]\_bfs, h\_[link1]\_[link2], H\_[link]\_bfs, H\_[link1]\_[link2] & Cartesian & Assymetric ($h$) or symmetric ($H$) hausdorff distance between 3D cartesian path traced by [link] in \tj{} w.r.t BFS path or between 3D Cartesian path traced by [link1] and [link2] in \tj{}\\
\hline
[link]\_bfs\_dtw, [link1]\_[link2]\_dtw & Cartesian & DTW cost between path traced by [link] in \tj{} and the BFS path, or between 3D-cartesian-path traced by [link1] and [link2] in \tj{}\\
\hline
\end{tabular}
}
\caption{Decoding of feature names into descriptions}
\end{table}

\begin{figure}[h]
\centering
\begin{tabular}{c|p{0.4\columnwidth}p{0.4\columnwidth}}
& Low feature-value & High feature-value \\
\hline
\rot{wrist\_tool\_dtw} & 
\adjincludegraphics[trim={.1\width} {.080\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{low}{0}} & 
\adjincludegraphics[trim={.2\width} {.0\height} {.2\width} {.15\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{high}{0}} \\

@@

\rot{wrist\_bfs\_dtw} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{high}{0}} \\
\end{tabular}
\caption{Trajectory examples of the most useful features, where the feature is displayed row-wise and columns are whether the feature is {\em low} or {\em high} for the example.}\label{fig:example_features}
\end{figure}

>>>>

This paper is organized as follows. In Section~\ref{sec:background}, we first describe related work in this area. In Section~\ref{sec:survey}, we present details of the online survey including information about the types of trajectories and environments used. Section~\ref{sec:raw_results} presents the results from the survey and analysis, including the trajectory features used for classification and the classification approaches used with the data. In Section~\ref{sec:conclusion}, we conclude with a discussion of how our results could be used to design motion planners that generate more human-acceptable trajectories. 
\begin{figure}
\centering
\begin{tabular}{c|c}
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{1}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{1}} \\
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{3}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{3}} \\
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{5}} &
\adjincludegraphics[trim = 100mm 0mm 100mm 30mm, width=0.44\columnwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{5}} \\
(a) & (b) \\
\end{tabular}
%\begin{minipage}[][][s]{0.45\columnwidth}
%\centering
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{1}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{2}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{3}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{4}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\gta{2014_Sep_17_18_40_15}{2}{5}}
%(a)
%\end{minipage}
%\hfill
%\vline
%\hfill
%\begin{minipage}[][][s]{0.45\columnwidth}
%\centering
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{1}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{2}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{3}}
%%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{4}}
%\includegraphics[trim = 100mm 0mm 100mm 30mm, width=\textwidth, clip=true]{\bta{2014_Sep_17_18_40_21}{2}{5}}
%(b)
%\end{minipage}
\caption{Example trajectory snapshots for motions that survey participants rated (a) highly and (b) poorly. In (b) the hand of the robot ducks under the table in between the first and middle snapshot.}\label{fig:example_trajectory}
\end{figure}

@@

\begin{table}
\label{tab:feature_description}
\scalebox{0.9}{
\centering
\begin{tabular}{|p{0.3\columnwidth}|p{0.2\columnwidth}|p{0.5\columnwidth}|}
\hline
Feature Name & Metric & Feature Description \\
\hline
path\_length, smoothness, clearance, max\_lin\_acc, joint\_limit\_distance & Joint-space & Features discussed in Section~\ref{subsec:traj_feat} computed on joint-space trajectory \tj{}\\
\hline
[link]\_length, [link]\_smoothness, [link]\_max\_curvature, [link]\_lin\_acc, [link]\_quat\_dist & Cartesian & Features discussed in Section~\ref{subsec:traj_feat} computed on 3D cartesian path traced by [link] in \tj{}\\
\hline
h\_[link]\_bfs, h\_[link1]\_[link2], H\_[link]\_bfs, H\_[link1]\_[link2] & Cartesian & Assymetric ($h$) or symmetric ($H$) hausdorff distance between 3D cartesian path traced by [link] in \tj{} w.r.t BFS path or between 3D Cartesian path traced by [link1] and [link2] in \tj{}\\
\hline
[link]\_bfs\_dtw, [link1]\_[link2]\_dtw & Cartesian & DTW cost between path traced by [link] in \tj{} and the BFS path, or between 3D-cartesian-path traced by [link1] and [link2] in \tj{}\\
\hline
\end{tabular}
}
\caption{Decoding of feature names into descriptions}
\end{table}

\begin{figure}[h]
\centering
\begin{tabular}{|c|cc|}%p{0.4\columnwidth}p{0.4\columnwidth}}
\hline
& Low feature-value & High feature-value \\
\hline
\rot{wrist\_tool\_dtw} & 
\adjincludegraphics[trim={.1\width} {.080\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{low}{0}} & 
\adjincludegraphics[trim={.2\width} {.0\height} {.2\width} {.15\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{high}{0}} \\

@@

\rot{wrist\_bfs\_dtw} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{high}{0}} \\
\hline
\end{tabular}
\caption{Trajectory examples of the most useful features, where the feature is displayed row-wise and columns are whether the feature is {\em low} or {\em high} for the example.}\label{fig:example_features}
\end{figure}
